---
title: "Dynamic Measurement Invariance Cutoffs for Dependent Groups"
author: "Created by Daniel McNeish and Melissa G Wolf"
date: "`r Sys.Date()`"
output:  pdf_document

params:
  data: NA
  name: NA
  Scale: NA
  Reps: NA
  Factors: NA
  missing: NA
  Groups: NA
  PD: 0
  MI: 0
  fit: NA
  Del: NA
  cutoffs: NA
---

```{r setup, include=FALSE}
library(knitr)
knitr::opts_chunk$set(echo = FALSE)
```


### Basic Information

**Dataset:** `r  paste(params$name)`

**Sample Size:** `r  paste(nrow(data()))`

**Missing Data Indicator:** `r paste(params$missing)`

**Invariance Constraints Tested:** `r paste(params$MI)`

**Number of Groups:** `r paste(params$Groups)`

```{r include=F}
if (input$Scale == "N"){
  scale<-paste("Continuous (Normal)")
  }
  if (input$Scale == "L"){
   scale<-paste("Ordinal/Likert Treated as Continuous")
  }
```

**Response Scale:** `r scale`


**Estimator:** `r input$est`

```{r include=FALSE}

  if (input$Reps == 100){
  precision<-paste("Exploratory")
  }
  
  if (input$Reps == 1000){
  precision<-paste("Full")
  }

if (input$Reps == 10){
  precision<-paste("Developer Test")
  }

```
**Cutoff Precision:** `r precision`


### Path Diagram of Your Configural Model:

```{r}
plot(params$PD)
```

### Your Model Fit Indices:

```{r, results='asis'}
kable(round(params$fit,3))
```

### Your Fit Index Differences:

```{r, results='asis'}
kable(round(params$Del,3))
```

### Your DMI Cutoffs:

```{r, results='asis'}
kable(round(params$cutoffs,3))
```


### Citation Recommendations:

**To cite this software:**

McNeish, D. & Wolf, M. G. (2024). Dynamic Measurement Invariance Cutoffs. R Shiny application [Software], version 0.0.0. www.dynamicfit.app.

Wolf, M.G. & McNeish, D. (2023). dynamic: An R package for deriving dynamic fit index cutoffs for factor analysis. Multivariate Behavioral Research, 58 (1), 189-194.

**To cite the method:**

McNeish, D. (under review). Dynamic Measurement Invariance Cutoffs for Longitudinal and Dyadic Data. 

McNeish, D. (2025). Dynamic measurement invariance cutoffs for two-group fit index differences.Psychological Methods. 

McNeish, D. & Wolf, M.G. (2023). Dynamic fit index cutoffs for confirmatory factor analysis models. Psychological Methods, 28 (1), 61-88.

